% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
\documentclass{article}

% ============================================================================
% 1. PREAMBLE
% ============================================================================
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}
\usepackage{mathptmx} % Times New Roman font
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}

% No page number on the cover
\pagenumbering{gobble}

% ============================================================================
% 2. DOCUMENT BODY
% ============================================================================
\begin{document}

% --- CONTACT INFO BLOCK (Top Left) ---
\begin{singlespace}
\textbf{Seth Sturm}\\
377 Messer Run Rd\\
Metz, WV 26585\\
+1 (681) 526-7605\\
sethsturm@gmail.com

\vspace{0.5em}

\textbf{Mary Ann Claytor}\\
221 Oliver St\\
St. Albans, WV 25177\\
+1 (304) 993-1939\\
maryannclaytor@gmail.com

\vspace{0.5em}

Grievants, \textit{pro se}
\end{singlespace}

\vspace{1.5cm}

% --- COURT HEADER ---
\begin{center}
    \textbf{\large BEFORE THE RULES AND BYLAWS COMMITTEE}\\
    \textbf{\large OF THE DEMOCRATIC NATIONAL COMMITTEE}
\end{center}

\vspace{1cm}

% --- CAPTION BLOCK ---
\noindent
\begin{tabularx}{\textwidth}{@{} p{0.45\textwidth} c p{0.5\textwidth} @{}}
    & : & \\
    \textbf{SETH STURM} and \textbf{MARY ANN CLAYTOR}, & : & Filing Date: December 12, 2025 \\
    & : & \\
    \hspace{1cm} Grievants, & : & \textbf{VERIFIED FORMAL CHALLENGE} \\
    & : & \\
    \hspace{0.5cm} v. & : & Relief Requested: \\
    & : & (a) Appointment of Independent Hearing Officer \\
    \textbf{WEST VIRGINIA DEMOCRATIC PARTY}; & : & (b) Interim reinstatement pending IHO determination \\
    \textbf{WEST VIRGINIA STATE DEMOCRATIC} & : & (c) Mandatory Recusal of conflicted members \\
    \textbf{EXECUTIVE COMMITTEE}; & : & (d) Written findings and recommendations for discipline \\
    \textbf{RULES AND BYLAWS COMMITTEE}, & : & \\
    & : & Recusal Requested For: \\
    \hspace{1cm} Respondents. & : & Harold Ickes (RBC Member) \\
    & : & James Roosevelt Jr. (RBC Co-Chair) \\
\end{tabularx}

\newpage
% Turn page numbering back on for the rest of the doc
\pagenumbering{arabic}

\newpage
\tableofcontents
\newpage

\section{PRELIMINARY STATEMENT}

\begin{enumerate}[series=mainlist, label=\arabic*., leftmargin=0.5in]
\item This Challenge targets two governance failures. First, the State Executive Committee ("WVSDEC") nullified the results of state-certified elections by removing members under an internal attendance policy. Second, Respondents rigged the formation of the Affirmative Action Committee ("AAC") by installing officers before the voting constituencies existed.

\item The WVSDEC removal of elected members violates the property rights established in \textit{State ex rel. Cornelius v. Warner}. In West Virginia, the legislature sets the term of office for executive committee members at four years. The State Party lacks the authority to shorten this statutory term via internal rule. Any policy that permits the summary removal of elected members subverts the will of the voters. Consequently, the removals are void regardless of procedure.

\item The AAC formation violated the 2020 Memorandum of Understanding ("MOU"). Respondents selected officers thirty-four days before the caucuses formed to elect them. Additionally, party leaders distributed internal scripts containing pre-written nominations for positions absent from the public agenda. This conduct violated the contractual mandate for an "open and transparent process."

\item Forensic metadata identifies RBC Member Harold Ickes as the author of the grievance and governance documents used to execute these actions. The metadata lists Ickes as "Author" on files submitted by local members. This undisclosed involvement creates a structural conflict of interest for the Rules and Bylaws Committee.

\item In Alabama, the RBC appointed an Independent Hearing Officer ("IHO") to cure identical defects. Grievants demand the same remedy. This Committee must halt the unlawful WVSDEC removals and order a compliant AAC formation process. Fair adjudication requires the mandatory recusal of conflicted members and the appointment of an IHO.
\end{enumerate}

\section{NATURE OF THE ACTION}

\begin{enumerate}[resume=mainlist]
\item This Challenge addresses the systemic violation of democratic rights.

\item The DNC has enabled procedural irregularities that disenfranchise elected members.

\item The current governance bodies possess fatal defects. The AAC is void \textit{ab initio} due to bad-faith formation. The WVSDEC is compositionally illegitimate due to unlawful removals.

\item Grievants seek enforcement of the 2020 Memorandum of Understanding and DNC Charter to cure these defects.
\end{enumerate}

\section{I. JURISDICTION AND TIMELINESS}

\textbf{Basis for Jurisdiction}

\begin{enumerate}[resume=mainlist]
\item The 2020 Memorandum of Understanding bears the signatures of RBC Co-Chairs James Roosevelt Jr. and Lorraine Miller [Exhibit T].

\item The MOU constitutes a written agreement supported by consideration [Exhibit T].

\item The MOU preamble establishes RBC jurisdiction over "party officers and positions" and "general compliance" [Exhibit T].
\end{enumerate}

\textbf{Timeliness}

\begin{enumerate}[resume=mainlist]
\item The WVSDEC removed members in May 2025 [Exhibit L]. The Board of Appeals issued rulings on September 25, 2025 [Exhibit E]. This filing occurs within twelve months of these events.

\item The June 28, 2024 RBC dismissal [Exhibit Z] documents the exhaustion of remedies.

\item The AAC has failed to meet since May 2023 [Exhibit AA]. This constitutes an ongoing violation.
\end{enumerate}

\section{II. PARTIES}

\textbf{Grievants}

\begin{enumerate}[resume=mainlist]
\item \textbf{Seth Sturm} is a registered Democrat and Founding Chair of the WVDP Indigenous Caucus.

\item \textbf{Mary Ann Claytor} is a registered Democrat, Chair of the WVDP Black Caucus, and a duly elected member of the WVSDEC from the 7th Senatorial District.
\end{enumerate}

\textbf{Respondents}

\begin{enumerate}[resume=mainlist]
\item \textbf{West Virginia Democratic Party (WVDP)} is a political association organized under the laws of West Virginia.

\item \textbf{West Virginia State Democratic Executive Committee (WVSDEC)} is the governing body established by West Virginia Code \S~3-1-9.
\end{enumerate}

\textbf{State Officials (Notice and Accountability)}

\begin{enumerate}[resume=mainlist]
\item \textbf{Mike Pushkin} is the State Chair of the WVDP.

\item \textbf{Selina Vickers} is the Challengers' representative under the 2020 MOU and Female Co-Chair of the AAC.
\end{enumerate}

\textbf{National Officials (Remedial and Disciplinary Relief)}

\begin{enumerate}[resume=mainlist]
\item \textbf{Harold Ickes} is a member of the Rules and Bylaws Committee.

\item \textbf{Clara Pratte} is a DNC official who participated in the 2023 mediation communications [Exhibit N].

\item \textbf{Ken Martin} served as DNC Vice Chair during the 2023 mediation period [Exhibit N].

\item \textbf{James Roosevelt Jr.} is an RBC Co-Chair and signatory to the June 28, 2024 dismissal [Exhibit Z].
\end{enumerate}

\section{III. ISSUES PRESENTED}

\begin{enumerate}[resume=mainlist]
\item Whether the June 2, 2021 AAC formation violated MOU \S~2.B.c and is void \textit{ab initio}.

\item Whether the removal of elected WVSDEC members violates the property rights established in \textit{Cornelius} and West Virginia Code \S~3-1-9.

\item Whether RBC Member Harold Ickes' undisclosed authorship of governance documents creates a structural conflict requiring recusal.

\item Whether the RBC must appoint an Independent Hearing Officer to apply uniform enforcement standards.
\end{enumerate}

\section{IV. STATEMENT OF FACTS}

\textbf{A. The 2020 Memorandum of Understanding}

\begin{enumerate}[resume=mainlist]
\item The 2020 MOU settled Credentials Committee challenges [Exhibit T].

\item Challengers withdrew challenges in exchange for the MOU terms [Exhibit T].

\item The MOU designated Selina Vickers as Challengers' representative [Exhibit T].

\item The MOU mandated an "open and transparent process" and RBC supervision [Exhibit T].

\item Section 2.B.c required that AAC members "be selected by their particular caucus" [Exhibit T].
\end{enumerate}

\textbf{B. The June 2, 2021 Script and AAC Formation}

\begin{enumerate}[resume=mainlist]
\item Vickers distributed Alabama Democratic Party Bylaws to caucus chairs on June 1, 2021 [Exhibit AF].

\item Vickers emailed caucus chairs: "I'm attaching a plain agenda and a separate agenda with a script built in" [Exhibit AF].

\item Vickers instructed: "The script should be considered an 'internal' document and should not be shared" [Exhibit AF].

\item Vickers instructed: "Push for a vote and no amendments" [Exhibit AF].

\item The script contained the nomination of Kim Felix as Latino Caucus representative [Exhibit C].

\item The script contained the nomination of Vickers for Parliamentarian/Secretary [Exhibit C].

\item The script contained pre-written praise for Vickers: "I can think of no one else remotely qualified" [Exhibit C].

\item The Latino Caucus formed on July 6, 2021, thirty-four days after the script named Felix as representative [Exhibit B].

\item The Board of Appeals found that "the AAC did not follow the approved procedure to notice nominations" [Exhibit F].

\item The Party applied no remedy [Exhibit F].
\end{enumerate}

\textbf{C. Forensic Metadata and RBC Member Involvement}

\begin{enumerate}[resume=mainlist]
\item Grievants analyzed document metadata using ExifTool [Exhibits AP--AU].

\item Metadata for the November 22, 2020 grievance lists "Harold Ickes" as Author [Exhibit AP].

\item Metadata for the July 3, 2021 grievance lists "Harold Ickes" as Author [Exhibit AU].

\item Metadata for the AAC Code of Conduct lists "Harold Ickes" as Author [Exhibit AS].

\item Ickes stated in a September 22, 2021 meeting: "I've said to Selina god knows how many times... at bottom you gotta out vote" [Exhibit A].
\end{enumerate}

\textbf{D. Indigenous Caucus Dissolution}

\begin{enumerate}[resume=mainlist]
\item The Indigenous Caucus dissolved on September 12, 2022 [Exhibit V].

\item The resolution states AAC leaders "invited Harold Ickes... to participate in all planning... and sought advice on how to silence minorities" [Exhibit V].
\end{enumerate}

\textbf{E. The Attendance Policy and May 2025 Removals}

\begin{enumerate}[resume=mainlist]
\item WVSDEC members Thornton Cooper and Richie Robb filed a grievance on July 15, 2024 warning that the Attendance Policy violated state law [Exhibit X].

\item The Board of Appeals dismissed the grievance for lack of standing [Exhibit Y].

\item The Party removed elected WVSDEC members, including Grievant Claytor, in May 2025 [Exhibit L].

\item State Chair Pushkin stated the removal was "effective immediately upon issuance of the notice" [Exhibit L].

\item The Party held no pre-deprivation hearings.
\end{enumerate}

\textbf{F. The September 25, 2025 Board of Appeals Hearing}

\begin{enumerate}[resume=mainlist]
\item Claytor filed a formal grievance challenging the policy under \textit{Cornelius} [Exhibit M].

\item The Board rejected the appeal but granted a "hardship waiver" [Exhibit E].

\item The Board ignored the substantive challenge to the policy's legality.

\item The phrase "hardship waiver" appears in no governing document.
\end{enumerate}

\textbf{G. Continuing AAC Dysfunction}

\begin{enumerate}[resume=mainlist]
\item The AAC has failed to meet since May 2023 [Exhibit AA].

\item Disability Caucus Parliamentarian John Doyle resigned on November 22, 2025 after documenting leadership's failure to respond [Exhibit AD].
\end{enumerate}

\section{FIRST CAUSE OF ACTION: BREACH OF THE 2020 MEMORANDUM OF UNDERSTANDING}

\begin{enumerate}[resume=mainlist]
\item Grievants re-allege all preceding paragraphs.
\end{enumerate}

\textbf{Breach I: Usurpation of Selection Authority}

\begin{enumerate}[resume=mainlist]
\item MOU Section 2.B.c requires that representatives be "selected by their particular caucus." On June 4, 2021, Kim Felix signed a letter to the DNC Chair as "AAC Co-Chair".

\item The Latino Caucus formed on July 6, 2021 [Exhibit B]. Consequently, the officer assumed authority thirty-four days before the selecting constituency existed. Existence of the constituency is a prerequisite for exercising selection rights. This action appointed the representative by fiat, violating the MOU.
\end{enumerate}

\textbf{Breach II: Violation of Notice (Self-Dealing)}

\begin{enumerate}[resume=mainlist]
\item The MOU Preamble guarantees "practical, proper, and effective notice." Selina Vickers scripted her own nomination for Parliamentarian/Secretary, a position absent from the agenda.

\item Vickers distributed a script containing the nomination and self-authored praise: "I can think of no one else remotely qualified" [Exhibit C]. Vickers concealed the position from the agenda and pre-arranged her acclamation. This denied eligible members the right to run.
\end{enumerate}

\textbf{Breach III: Suppression of Open Process}

\begin{enumerate}[resume=mainlist]
\item The MOU mandates an "open and transparent process." Vickers distributed formation documents marked "internal" and instructed chairs: "Push for a vote and no amendments" [Exhibit AF].

\item A secret script violates transparency. The instruction to block amendments stripped members of their right to deliberate.
\end{enumerate}

\textbf{Claim for Relief}

\begin{enumerate}[resume=mainlist]
\item Respondents breached the MOU by usurping selection authority, suppressing notice, and conducting secret proceedings.

\item These breaches render the AAC \textbf{void \textit{ab initio}}. The Committee must \textbf{declare the formation invalid} and \textbf{order new elections} under IHO supervision.
\end{enumerate}

\section{SECOND CAUSE OF ACTION: DENIAL OF DUE PROCESS}

\begin{enumerate}[resume=mainlist]
\item Grievants re-allege all preceding paragraphs.

\item West Virginia Code \S~3-1-9 sets the term of State Executive Committee members at four years. In \textit{State ex rel. Cornelius v. Warner}, the court ruled that "duly elected party county executive committee members cannot be removed from office without due process." [cite_start]The court held that summary removal overrides the will of the voters, "thereby subverting the democratic process" [Exhibit W] [cite: 319-321].
\end{enumerate}

\textbf{Claim for Relief}

\begin{enumerate}[resume=mainlist]
\item Respondents violated the rights of elected members. The State Party utilized an internal attendance policy to shorten a statutory four-year term.

\item The State Party lacks the authority to override the legislature or "subvert[] the democratic process." Consequently, the attendance policy is ultra vires and the removals are void. The Committee must order the \textbf{immediate reinstatement} of all affected members.
\end{enumerate}

\section{THIRD CAUSE OF ACTION: VIOLATION OF WEST VIRGINIA CODE}

\begin{enumerate}[resume=mainlist]
\item Grievants re-allege all preceding paragraphs.

\item West Virginia Code \S~3-1-9(f) assigns vacancy-filling authority to county executive committees. The Board of Appeals utilized "hardship waivers" to restore selected members.
\end{enumerate}

\textbf{Claim for Relief}

\begin{enumerate}[resume=mainlist]
\item Respondents violated state law by exercising vacancy-filling authority assigned to county committees.

\item The Board of Appeals acted without statutory or bylaw authority. The Committee must issue \textbf{declaratory relief} prohibiting the Board from altering the composition of the statutory body.
\end{enumerate}

\section{FOURTH CAUSE OF ACTION: DISPARATE ENFORCEMENT}

\begin{enumerate}[resume=mainlist]
\item Grievants re-allege all preceding paragraphs.

\item The RBC appointed an Independent Hearing Officer in Alabama to address identical governance structures and violations involving the same RBC member.
\end{enumerate}

\textbf{Claim for Relief}

\begin{enumerate}[resume=mainlist]
\item The refusal to apply the same remedy in West Virginia constitutes disparate enforcement. The Committee must appoint an \textbf{Independent Hearing Officer} to apply the "Alabama Standard" and investigate the documented violations.
\end{enumerate}

\section{FIFTH CAUSE OF ACTION: STRUCTURAL CONFLICT OF INTEREST}

\begin{enumerate}[resume=mainlist]
\item Grievants re-allege all preceding paragraphs.

\item Document metadata identifies RBC Member Harold Ickes as the author of grievances and governance documents filed by local members.
\end{enumerate}

\textbf{Claim for Relief}

\begin{enumerate}[resume=mainlist]
\item A supervisor cannot secretly author documents for a supervised party. This creates a structural conflict of interest. The Committee must \textbf{order the mandatory recusal} of Harold Ickes and \textbf{appoint an Independent Hearing Officer} insulated from this conflict.
\end{enumerate}

\section{PRAYER FOR RELIEF}

\begin{enumerate}[resume=mainlist]
\item WHEREFORE, Grievants seek the following relief:
\end{enumerate}

\textbf{A. Declaratory Relief}
\begin{enumerate}[label=\roman*., nosep, leftmargin=0.5in]
    \item Declare the June 2, 2021 AAC formation void \textit{ab initio};
    \item Declare the Attendance Policy and May 2025 removals void as violative of \textit{Cornelius} and state law.
\end{enumerate}

\textbf{B. Injunctive Relief}
\begin{enumerate}[label=\roman*., nosep, leftmargin=0.5in]
    \item Order the immediate reinstatement of all WVSDEC members removed under the Attendance Policy.
    \item Enjoin Harold Ickes from participation in this challenge.
    \item Require recusal of RBC Co-Chair James Roosevelt Jr.
\end{enumerate}

\textbf{C. Equitable Relief}
\begin{enumerate}[label=\roman*., nosep, leftmargin=0.5in]
    \item Appoint an Independent Hearing Officer.
    \item Order new AAC elections under RBC supervision.
\end{enumerate}

\textbf{D. Referrals}
\begin{enumerate}[label=\roman*., nosep, leftmargin=0.5in]
    \item Refer RBC member conduct for investigation.
    \item Suspend party-building funds until compliance is certified.
\end{enumerate}

\section{DEMAND FOR HEARING}

\begin{enumerate}[resume=mainlist]
\item Grievants demand a hearing before the Rules and Bylaws Committee or its designated Independent Hearing Officer.
\end{enumerate}

\section{VERIFICATION}

\textbf{Declaration of Seth Sturm}

I, Seth Sturm, declare under penalty of perjury that I have read the foregoing Verified Formal Challenge and the facts stated herein are true and correct to the best of my knowledge.

\vspace{1cm}
\noindent Executed on: December 12, 2025

\vspace{1cm}
\noindent \makebox[3in]{\hrulefill}\\
Seth Sturm, Grievant

\vspace{1cm}

\textbf{Declaration of Mary Ann Claytor}

I, Mary Ann Claytor, declare under penalty of perjury that I have read the foregoing Verified Formal Challenge and the facts stated herein are true and correct to the best of my knowledge.

\vspace{1cm}
\noindent Executed on: December 12, 2025

\vspace{1cm}
\noindent \makebox[3in]{\hrulefill}\\
Mary Ann Claytor, Grievant

\section{EXHIBIT LIST}

\begin{description}
    \item[{[Exhibit A]}] \textbf{September 22, 2021 Video/Transcript (Ickes)}
    \item[{[Exhibit B]}] \textbf{June 2, 2021 AAC Meeting Transcript}
    \item[{[Exhibit C]}] \textbf{June 2, 2021 Script}
    \item[{[Exhibit D]}] \textbf{August 17, 2021 AAC Meeting Transcript}
    \item[{[Exhibit E]}] \textbf{September 25, 2025 BOA Hearing Video/Transcript}
    \item[{[Exhibit F]}] \textbf{WVDP Board of Appeals Resolution (November 29, 2021)}
    \item[{[Exhibit G]}] \textbf{Mary Ann Claytor Email (September 1, 2021)}
    \item[{[Exhibit H]}] \textbf{Mary Ann Claytor Email (September 20, 2021)}
    \item[{[Exhibit I]}] \textbf{Email Chain on AAC Agenda (September 15, 2021)}
    \item[{[Exhibit J]}] \textbf{Sturm-Bush Correspondence (November 12, 2021)}
    \item[{[Exhibit K]}] \textbf{Mary Ann Claytor Email (September 23, 2021)}
    \item[{[Exhibit L]}] \textbf{State Chair Pushkin Correspondence (May 30, 2025)}
    \item[{[Exhibit M]}] \textbf{Mary Ann Claytor Formal Grievance (July 28, 2025)}
    \item[{[Exhibit N]}] \textbf{DNC Official Clara Pratte Correspondence (August 2023)}
    \item[{[Exhibit O]}] \textbf{DNC Official Clara Pratte Correspondence (September 2023)}
    \item[{[Exhibit P]}] \textbf{DNC Official Clara Pratte Correspondence (October 2023)}
    \item[{[Exhibit Q]}] \textbf{DNC Official Clara Pratte Correspondence (December 2023)}
    \item[{[Exhibit R]}] \textbf{December 2023 SEC Meeting Transcript}
    \item[{[Exhibit S]}] \textbf{March 18, 2024 SEC Hearing Transcript}
    \item[{[Exhibit T]}] \textbf{2020 Memorandum of Understanding}
    \item[{[Exhibit U]}] \textbf{WVDP Motion to Dismiss (2023)}
    \item[{[Exhibit V]}] \textbf{Indigenous Caucus Resolution of Dissolution}
    \item[{[Exhibit W]}] \textbf{State ex rel. Cornelius v. Warner Decision (2022)}
    \item[{[Exhibit X]}] \textbf{Cooper \& Robb Appeal (July 15, 2024)}
    \item[{[Exhibit Y]}] \textbf{Board of Appeals Written Opinion (June 23, 2025)}
    \item[{[Exhibit Z]}] \textbf{June 28, 2024 RBC Rejection Letter}
    \item[{[Exhibit AA]}] \textbf{Disability Caucus Correspondence (January-July 2025)}
    \item[{[Exhibit AB]}] \textbf{AAC Election Ballot (June 15, 2022)}
    \item[{[Exhibit AC]}] \textbf{Disability Caucus Correspondence (June 19, 2025)}
    \item[{[Exhibit AD]}] \textbf{Disability Caucus Resignation (November 22, 2025)}
    \item[{[Exhibit AE]}] \textbf{Vickers Website (Wayback Machine)}
    \item[{[Exhibit AF]}] \textbf{Vickers Emails (May 31--June 1, 2021)}
    \item[{[Exhibit AG]}] \textbf{Robert Baker Email (August 20, 2021)}
    \item[{[Exhibit AH]}] \textbf{Vickers Email (September 26, 2021)}
    \item[{[Exhibit AI]}] \textbf{Black Caucus Script (June 1, 2021)}
    \item[{[Exhibit AJ]}] \textbf{Vickers Strategic Coaching (June 3, 2021)}
    \item[{[Exhibit AK]}] \textbf{Vickers Strategic Framing Email (June 1, 2021)}
    \item[{[Exhibit AL]}] \textbf{Resolution of Diversity Caucuses with Metadata}
    \item[{[Exhibit AM]}] \textbf{Black Caucus Agenda (June 15, 2021)}
    \item[{[Exhibit AN]}] \textbf{Ickes Grievance Draft with Metadata (July 3, 2021)}
    \item[{[Exhibit AO]}] \textbf{Questions to Consider}
    \item[{[Exhibit AP]}] \textbf{November 22, 2020 Grievance with Metadata}
    \item[{[Exhibit AQ]}] \textbf{August 16, 2021 AAC Agenda with Metadata}
    \item[{[Exhibit AR]}] \textbf{August 17, 2021 Procedural Rules with Metadata}
    \item[{[Exhibit AS]}] \textbf{September 11, 2021 Code of Conduct with Metadata}
    \item[{[Exhibit AT]}] \textbf{September 15, 2021 AAC Agenda with Metadata}
    \item[{[Exhibit AU]}] \textbf{July 3, 2021 Final Grievance with Metadata}
    \item[{[Exhibit AV]}] \textbf{Alabama Independent Hearing Officer Appointment}
    \item[{[Exhibit AW]}] \textbf{RBC Alarm Over Alabama Violations}
    \item[{[Exhibit AX]}] \textbf{AAC Email Chain (August 2021)}
    \item[{[Exhibit AY]}] \textbf{Bylaws Subcommittee Report (September 2021)}
    \item[{[Exhibit AZ]}] \textbf{Vickers Ghostwriting Email (August 17, 2021)}
    \item[{[Exhibit BA]}] \textbf{Assadzandi Social Media Coordination (August 21, 2021)}
    \item[{[Exhibit BB]}] \textbf{Clifford Coordination Email (August 22, 2021)}
    \item[{[Exhibit BC]}] \textbf{Disability Resolution and Correspondence (September 2021)}
    \item[{[Exhibit BD]}] \textbf{AAC Letter to State Chair (December 5, 2021)}
    \item[{[Exhibit BE]}] \textbf{WVDP Motion to Dismiss (July 24, 2023)}
    \item[{[Exhibit BF]}] \textbf{Betty Rivard Email (August 2021)}
\end{description}

\end{document}